MS Prelim Data K23

### 2022-03-22 K23_prelim_data_started_20220225.Rmd
graphs

#visreg
#sapply(fascicle_age_lm,visreg)
```

@@

plot <- ggplot(df_for_visreg, aes(x=diagnosis, y = prop_lost, col=diagnosis)) +
  geom_violin() + 
  geom_jitter(shape=16, position=position_jitter(0.05)) + 
  geom_boxplot(width=0.1) + theme_minimal() + 
  stat_summary(fun.y=median, geom="point", size=2, color="black") + 
  scale_x_discrete(labels=c("1" = "Depressed", "2" = "Non-Depressed"))

@@

#bar plot
Diagnosis <- c("Depressed", "Non-Depressed")
value <- c(mean(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2]),
           mean(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1]))

@@

# Grouped
barplot <- ggplot(data, aes(x=Diagnosis,fill=Diagnosis, y=value)) + 
  geom_bar(stat="identity", position=position_dodge(0.9)) + 
    geom_errorbar(aes(ymin=value-sem, ymax=value+sem), width=.1, position=position_dodge(0.9)) + 
  ylab("Proportion of Fascicles Affected") +
  theme(axis.text = element_text(size = 12, colour = "black"))

@@

Diagnosis <- c(rep("Depressed" , 2) , rep("Non-Depressed" , 2))
Fascicle <- rep(c("Arcuate Fasciculus" , "Superior Cerebellar Peduncle"), 2)
value <- c(mean(dep_and_healthy_groups_for_ICD_analysis$AF_R[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2]),
           mean(dep_and_healthy_groups_for_ICD_analysis$SCP[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2]),
           mean(dep_and_healthy_groups_for_ICD_analysis$AF_R[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1]),
           mean(dep_and_healthy_groups_for_ICD_analysis$SCP[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1]))

@@

@@

print(plot)
###### Depression network x depression group interaction - It is there, depression always worse. 
#these lms largely match up with the t.tests above. Sig differences between depressed (more disease) within and outside of mask

@@

>>>>

#visreg
#sapply(fascicle_age_lm,visreg)
visreg(fascicle_age_lm$AF_R,ylab = "Proportion of Affected Streamlines", xlab = "Age in Years",
       line=list(col="red"),
       points=list(col="black"))

@@

plot <- ggplot(df_for_visreg, aes(x=Diagnosis, y = prop_lost, col=Diagnosis)) +
  geom_violin() + 
  geom_jitter(shape=16, position=position_jitter(0.05)) + 
  geom_boxplot(width=0.1) + theme_minimal() + 
  stat_summary(fun.y=median, geom="point", size=2, color="black") + 
  scale_x_discrete(labels=c("1" = "Depressed", "2" = "Non-Depressed"))

@@

#bar plot
Diagnosis <- c("MS w/Depression", "MS No Depression")
value <- c(mean(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2]),
           mean(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1]))

@@

# Grouped
barplot <- ggplot(data, aes(x=Diagnosis,fill=Diagnosis, y=value)) + 
  geom_bar(stat="identity", position=position_dodge(0.9)) + 
    geom_errorbar(aes(ymin=value-sem, ymax=value+sem), width=.1, position=position_dodge(0.9)) + 
  ylab("Proportion of Fascicles Affected") +
  ylim(0,0.5) +
  theme(axis.text = element_text(size = 12, colour = "black"))

# Grouped
barplot <- ggplot(data, aes(x=reorder(Diagnosis, -value),fill=Diagnosis, y=value)) + 
  geom_bar(stat="identity", colour="black", width=0.8, size=1.5) + 
    geom_errorbar(aes(ymin=value-sem, ymax=value+sem), width=.1, position=position_dodge(0.9), size=1.5) +
  scale_fill_manual(values = c("#cdcdcd", "#FFFFFF")) + #comment out if you want colored graph
  ylab("Proportion of Fascicles Affected") +
  theme(axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank(), 
        axis.title.y = element_text(size=20),
        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
        panel.background = element_rect(colour = "white", fill = "white")) + #comment out if you want pretty 
  scale_y_continuous(expand = c(0, 0), limits = c(0, 0.52)) #comment out if you want colored graph

@@

Diagnosis <- c(rep("Depressed" , 2) , rep("Non-Depressed" , 2))
Fascicle <- rep(c("Depression Network (AF)" , "Non-depression network (SCP)"), 2)
value <- c(mean(dep_and_healthy_groups_for_ICD_analysis$AF_R[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2]),
           mean(dep_and_healthy_groups_for_ICD_analysis$SCP[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2]),
           mean(dep_and_healthy_groups_for_ICD_analysis$AF_R[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1]),
           mean(dep_and_healthy_groups_for_ICD_analysis$SCP[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1]))

@@

barplot2 <- ggplot(data, aes(fill=Diagnosis, y=value, x=Fascicle)) + 
    geom_bar(position="dodge", stat="identity", colour = "black", width=0.9,size=1.5) + 
    geom_errorbar(aes(ymin=value-sem, ymax=value+sem), width=.1, position=position_dodge(0.9), size=1.5) + 
    scale_fill_manual(values = c("#cdcdcd", "#FFFFFF", "#cdcdcd", "#FFFFFF")) + #comment out if you want colored graph

    ylab("Proportion of Fascicles Affected") +
    theme(axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank(), 
          axis.title.y = element_text(size=20),
          axis.line = element_line(size = 1.5, colour = "black", linetype=1),
          panel.background = element_rect(colour = "white", fill = "white")) + #comment out if you want pretty graph
    scale_y_continuous(expand = c(0, 0), limits = c(0, 0.52)) #comment out if you want colored graph

print(barplot2)

@@

########## Bar plot
Network <- c("Depression Network","Non-Depression Network")
value <- c(mean(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet),
           mean(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_nondep_network))

sem <- c((sd(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet)/sqrt(dim(dep_and_healthy_groups_for_ICD_analysis)[1])),
           (sd(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_nondep_network)/sqrt(dim(dep_and_healthy_groups_for_ICD_analysis)[1])))

data <- data.frame(Network,value,sem)
#data$Fascicle <- pretty_names

# Grouped
barplot <- ggplot(data, aes(x=Network,fill=Network, y=value)) + 
  geom_bar(stat="identity", position=position_dodge(0.9)) + 
  geom_errorbar(aes(ymin=value-sem, ymax=value+sem), width=.1, position=position_dodge(0.9)) + 
  ylab("Proportion of Fascicles Affected") +
  ylim(0,0.5) +
  theme(axis.text = element_text(size = 12, colour = "black"))

###### Depression network x depression group interaction - It is there, depression always worse. 
#these lms largely match up with the t.tests above. Sig differences between depressed (more disease) within and outside of mask

@@

### grouped bar and line plot

Diagnosis <- c(rep("Depressed" , 2) , rep("Non-Depressed" , 2))
Sex <- rep(c("Male" , "Female"), 2)
value <- c(mean(dep_and_healthy_groups_for_ICD_analysis$SLF1_L[(dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 1)]),
           mean(dep_and_healthy_groups_for_ICD_analysis$SLF1_L[(dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 2)]),
           mean(dep_and_healthy_groups_for_ICD_analysis$SLF1_L[(dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 1)]),
           mean(dep_and_healthy_groups_for_ICD_analysis$SLF1_L[(dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 2)]))

sem <- c((sd(dep_and_healthy_groups_for_ICD_analysis$SLF1_L[(dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 1)])/sqrt(sum((dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 1)))),
         (sd(dep_and_healthy_groups_for_ICD_analysis$SLF1_L[(dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 2)])/sqrt(sum((dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 2)))),
         (sd(dep_and_healthy_groups_for_ICD_analysis$SLF1_L[(dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 1)])/sqrt(sum((dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 1)))),
         (sd(dep_and_healthy_groups_for_ICD_analysis$SLF1_L[(dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 2)])/sqrt(sum((dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 2)))))

data <- data.frame(Diagnosis,Sex,value, sem)
#data$Fascicle <- pretty_names

# Grouped
barplot <- ggplot(data, aes(fill=Sex, y=value, x=Diagnosis)) + 
    geom_bar(position="dodge", stat="identity") + 
    geom_errorbar(aes(ymin=value-sem, ymax=value+sem), width=.1, position=position_dodge(0.9)) + 
  ylab("Proportion of SLF Affected") +
  theme(axis.text = element_text(size = 12, colour = "black"), axis.title.x = element_blank())

lineplot <- ggplot(data=data, aes(fill=Sex, y=value, x=Diagnosis, group = Sex)) +

    geom_line(aes(color=Sex, size=0.9)) +
    geom_point(aes(color=Sex, size=0.9)) +
    ylim(0.05,0.30)+
    ylab("Proportion of SLF Affected") +
    geom_errorbar(aes(ymin=value-sem, ymax=value+sem), width=.1) + 
    theme(axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank())

print(lineplot)
